Covid-19 A Spatio-Temporal Investigation.

### 2021-01-11 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 In opposition to the purely spatial scan statistic, the spatio-temporal scan statistic creates cylindrical windows in three dimensions, where the height is a representation of time,

>>>>

 In opposition to the purely spatial scan statistic, the spatio-temporal scan statistic creates cylindrical windows in three dimensions, where the height is a representation of time, the cylinders are flexible in their circular bases and initial dates...
